Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench

### 2021-09-10 paper/introduction.tex
Add contributions to the introduction

>>>>

\noindent \textbf{Contributions}:
This paper details the following contributions.
\begin{compactitem}
  \item  A Cryptol specification for \texttt{SHA3} that directly corresponds to the \texttt{FIPS} 202 specification and passes the test vectors provided by the same specification.
  \item A Cryptol specification based on the OpenSSL implementation of \texttt{SHA3} that uses a reordered state vector and precomputed tables in Keccak for performance gains and passes test vectors
  \item A \texttt{SAW} proof that the \texttt{FIPS} 202 specification is equivalent to the OpenSSL specification
  \item A \texttt{SAW} proof that the OpenSSL Keccak specification is equivalent to the OpenSSL C-implementation of the same function for all possible state vector input
  \item Early evidence that modular cryptographic specifications such as \texttt{SHA3} lend themselves to efficient \texttt{SAW} verification against C implementations as opposed to flattened specifications such as \texttt{SHA2} 
\end{compactitem}
